The Space of Feasible Execution Times for Asynchronous Periodic Task Systems using Definitive Idle Times

### 2013-09-23 dit-paper_ieee.tex
minor changes

	In other words, fig.~\ref{fig:sizeRatio}
	evaluates the feasibility gain of adding random offsets to a synchronous task
	set. It is assumed that a more advanced strategy to assign these offsets
	would yield a greater difference.

@@

	The ratio between the size of the synchronous and asynchronous C-spaces of
	these systems roughly range from 0.95 in the worst case (high utilization, high
	CDF) to 0.85 in the best case (low utilization, low CDF). As calculating those
	sizes is rather long, the number of systems used to obtain average
	results was rather low (1000), which is the likely cause of the spikes in the
	data. Note that the value of the CDF has a greater influence on this ratio than
	the system's total utilization, but less so when the CDF is lower. It is also
	important to note that even though a 0.95 ratio may not seem much, the
	synchronous C-spaces of the systems contain many dominated WCET vectors, and
	only those that are in the border (i.e. non-dominated) actually matter to the
	designer of the system. Using the asynchronous C-space instead will relax some
	constraints and therefore add new acceptable solutions that will dominate solutions that were previously non-dominated,
	increasing the quality of the C-space border.

>>>>

	In other words, fig.~\ref{fig:sizeRatio}
	evaluates the feasibility gain of adding random offsets to a synchronous task
	set. It is assumed that a more advanced strategy to assign these offsets (such
	as the ones from \cite{goossens2003scheduling}) would yield a
	greater difference.

@@

	The ratio between the size of the synchronous and asynchronous C-spaces of
	these systems roughly range from 0.95 in the worst case (high utilization, high
	CDF) to 0.85 in the best case (low utilization, low CDF). As calculating those
	sizes is rather long, the number of systems used to obtain average
	results was rather low (5000), which is the likely cause of the spikes in the
	data. Note that the value of the CDF has a greater influence on this ratio than
	the system's total utilization, but less so when the CDF is lower. It is also
	important to note that even though a 0.95 ratio may not seem much, the
	synchronous C-spaces of the systems contain many dominated WCET vectors, and
	only those that are in the border (i.e. non-dominated) actually matter to the
	designer of the system. Using the asynchronous C-space instead will relax some
	constraints and therefore add new acceptable solutions that will dominate solutions that were previously non-dominated,
	increasing the quality of the C-space border.
